Mahotas: Open source software for scriptable computer vision

### 2012-07-04 paper.tex
MIN Update download counts

It has been available in the Python Package Index since April~2010 and has been
downloaded over 5500~times. Mahotas is available as a FreeBSD package and is
under evaluation for inclusion in the Debian distribution (which will cause it
to be available as a native package for its derivatives, most famously Ubuntu).

@@

Mahotas includes code ported and incorporated from other projects. In
particular, the \textsc{surf} implementation is a port from the code from
\textit{dlib},\footnote{Dlib's webpage is at \url{http://dlib.net}.} a very
good \cpp{} library by Davis King. I also gleaned some insight into the
implementation of these features from Christopher Evan's OpenSURF library and
its documentation \citep{evans2009}.\footnote{OpenSURF is available at
\url{http://www.chrisevansdev.com/computer-vision-opensurf.html}, where several
documents describe details of the implementation.} The image loading code,
which interfaces with the FreeImage library, was written by Zachary Pincus and
some of the support code was written by Peter J. Verveer for the
\code{scipy.ndimage} project. All of these contributions were integrated while
respecting the software licenses under which the original code had been
released. Robert Webb, a summer student, worked with me on the local binary
patterns implementation. Finally, I thank the several users who have reported
bugs and submitted small fixes and participated on the project mailing list.

>>>>

It has been available in the Python Package Index since April~2010 and has been
downloaded over 20,000~times. This does not include any downloads from other
sources.

@@

Mahotas includes code ported and incorporated from other projects. In
particular, the \textsc{surf} implementation is a port from the code from
\textit{dlib},\footnote{Dlib's webpage is at \url{http://dlib.net}.} a very
good \cpp{} library by Davis King. I also gleaned some insight into the
implementation of these features from Christopher Evan's OpenSURF library and
its documentation \citep{evans2009}.\footnote{OpenSURF is available at
\url{http://www.chrisevansdev.com/computer-vision-opensurf.html}, where several
documents describe details of the implementation.} The code which interfaces
with the FreeImage library, was written by Zachary Pincus and some of the
support code was written by Peter J. Verveer for the \code{scipy.ndimage}
project. All of these contributions were integrated while respecting the
software licenses under which the original code had been released. Robert Webb,
a summer student, worked with me on the local binary patterns implementation.
Finally, I thank the several users who have reported bugs and submitted small
fixes and participated on the project mailing list.
